HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

\paragraph{Annotation.}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists\oa{were there no other annotators from Prague?}.

@@

Our annotation experiment sought to address the following questions:
\begin{itemize}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences.
\item Can HUME capture translation issues that other annotation schemes (such as adequacy judgements and HMEANT
cannot)?
\item What can HUME annotation tell us about the strengths and weaknesses of MT?
\end{itemize}

\bh{Maybe we should remove the third one, we
probably don't address it in this paper}

>>>>

@@

Our annotation experiment sought to address the following questions:
\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

\section{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists\oa{were there no other annotators from Prague? Ondrej
does not remember! Was it just Ondrej+Jana Sindlerova? Then it would be one
computer scientist and one linguist for Czech.}.
